\section{Chalmers Optical 213 Lamp}
  Follow the manual for startup.of lamp.
  \cmd{Power \quote{on} \ira when \quote{Ready} is shown press \quote{CP}\ira when \quote{start} is shown press \quote{start}}
 
  \subsection{Loading mask}
   \begin{enumerate}
   	\item \cmd{Get the correct chuck and attach it to the vacuum tube.} Pull on red screw to release the tube.
   	\item \cmd{Click \quote{change mask} \ira \quote{enter}} to turn off the vacuum;
    \item \cmd{Position mask in the check \ira \quote{enter}} to turn vacuum on \ira \cmd{slide the chuck into machine};
   \end{enumerate}

  \subsection{Loading program}
   \begin{itemize}
   	\item \cmd{\quote{Select program}\ira up and down arrows to select \quote{soft},\quote{loVac} etc\ira \quote{select program}} to stop selection. Soft, Hard, LoVac, Vac are in order of increasing lithography accuracy (from 3$ \mu m $ to 500nm);
   	\item \cmd{\quote{Edit program} \ira change \textbf{exposure time} and \textbf{working distance} (typically 20$ \mu m $), 10 sec pre vacuum\ira\quote{edit program}} to set.
   	\item \red{MAKE SURE THAT FLOOD IS OFF!! Or exposure will begin straight after loading};
   \end{itemize}

  \subsection{Loading samples}
   \begin{enumerate}
   	\item \cmd{Press \quote{load} \ira put sample on plate \ira \quote{Enter} to turn on vacuum \ira slide in \ira \quote{Enter} to raise the bar};
   	\item WEC performed (bringing plate to the mask);
   \end{enumerate}

  \subsection{Aligning}
   By this stage we should be in alignment mode. Choose \quote{split field option}, separate the objectives by turning handles on side of microscope, fine focus just above the lenses. Intensity also above lenses. Rotate microscope with knob on the top.
   \begin{enumerate}
   	\item \cmd{Turn dial \quote{TSA}};
   	\item \cmd{Use arrows to move to first marker \ira \quote{Set prefference} to remember position};
   	\item \cmd{Move to second marker \ira \quote{Scan}} to move back to first position;
   	\item \cmd{Turn X-Y dials to center the marker};
   	\item \cmd{Press \quote{scan} \ira move to second marker \ira turn Theta dial} so that pattern shift halfway to correct position \cmd{\ira \quote{scan} to move back to first marker;}
   	\item \cmd{Repeat above steps};
   	\item \cmd{Once alignment looks good enough press \quote{Alignment check} to bring sample close to mask \ira change magnification \ira\red{perform check!! BUT NO MOVEMENT} \ira press \quote{Alignment check} to move again.}
   	\item \red{PRESS EXPOSURE TO EXPOSE};
   \end{enumerate}
  
  Automatic unloading. \cmd{\quote{Change mask} \ira \quote{enter} \ira unload \ira \quote{TSA} off}.
 \newpage
 