\section{Chalmers Plasma etch}
  Machine is located next to three transparent \quote{MC2 tiles} in the floor. 
  
  \begin{itemize}
  	\item \cmd{Go to cupboard behind the main machine, and turn on the required valves;}
  	\item \cmd{Go onto screen \ira Press \quote{stop} \ira \quote{Vent} \ira Enter a name for the process (not very important);}
  	\item \cmd{Click \quote{process} \ira \quote{Recipe} \ira \quote{load} the correct recipe and overwrite\ira click and \quote{edit} process to change parameters;}
  	\item \cmd{Click \quote{run} \ira } two stages will occur, first the pumping of the main chamber and then the etching with the selected plasma.
  	\item \red{While pumping is occurring:} \cmd{Turn on camera switch \ira turn on camera monitor \ira turn on utility (from the back);}
  	\item Then tune the interferometer. Interferometer simply measure the interference between parts of the laser light, part of which reflects off the Paladium surface (not etched) and part of which reflects off the etched surface \ira \red{LASER LIGHT MUST BE PLACED ON THE EDGE OF THE THING THAT WILL BE ETCHED AND WHAT WILL REMAIN}. Every time the distance 
  	\begin{equation}
	  	d = \frac{\lambda}{2},
  	\end{equation} 
  	
  	\noindent the interference pattern will repeat, where $ \lambda $ is the frequency of the laser light. Thus we count the number of interference periods to ge the thickness.
  	
  	\cmd{To do so, put laser using the knobs onto wafer (readingA) and metal (readingB). Read off the voltage reading on the unit, tuning offset and sensitivity to get best response. Then position laser to get (responseA + responseB)/2;}
  	
  	\red{MAKE SURE THAT THE READING ON THE UNIT IS AROUND 5 - OTHERWISE WHEN OSCILLATIONS START THE READING COULD GO OUT OF RANGE!}
  	
  	\item \cmd{\red{When etching process starts, click \quote{interferogram} button to load the interferogram;}}
  	\item \cmd{Once done, click \quote{puase button to terminate process}};
  	\item \cmd{Once unloaded \ira \quote{stop} \ira \quote{evacuate} \ira unload \ira \quote{stop} \ira \quote{vent};} 
  	\item If you want another process straight after, then \cmd{\red{pump straight away! since it automatically starts venting!}}
  \end{itemize}

 \red{If special gasses where used, chamber must be cleaned. \cmd{Close all Chlorine taps behind machine \ira evacuate and run \quote{Clean Chamber 1 Chlorine} recipe.}}
  
 \newpage
 