% -*- TeX-master: "../fat_manual.tex" -*-
\section{RHUL The chook-chook}
Normal values:
\begin{itemize}
  \item Flow is 0.60mmol
  \item Low pressure near can - 4mBar
  \item When mixture injected, do not add more than 1200mBar. Pump it, then add
        some more from can
\end{itemize}

Mixture is injected and circulated

\begin{framed}\noindent
  Valve 2 - its the equlibrator for V1 - you need the same pressure on either
  side of V1, and you use V2 to do this. Then, the can open V1.
\end{framed}
\begin{framed}\noindent
  The cooling system is composed of two parts
  \begin{itemize}
    \item The pulse tube that fires in helium and expands it - it uses the big
          compressor in the shed.
    \item The circulating cycle of He3 that is pumped out of He4. This is the
          big contour on the right of the big screen. P3 monitors the pressure
          before the capillary constriction that this mixture is funneled
          through.
  \end{itemize}
\end{framed}

\subsection{Pumping}
System needs to be pumped to avoid formation of ice when it is cooled.
\begin{enumerate}
  \item Can load the two blueforce programs on the desktop or mash buttons on
        the big panel;
  \item \cmd{First stop venting by closing valves 14, 16, 19};
  \item \cmd{Close the cases, with the stitch facing the far wall of the lab};
  \item \cmd{Check the pressure is > 40Bar on the cylinder in the corner} and
        \cmd{80psi on the output} since this is used to operate the valves;
  \item \cmd{Refill the trap with nitrogen so its full}. The trap will absorb
        gases that are not Helium - they liquify? Eventually we need to
        replenish it;
  \item \cmd{Turn on the Scroll Pump 2 \ira V21, V16, V14} for rough pumping.
        \red{\cmd{Wait until \quote{P6} reads 1mbar}}.
  \item \textbf{Pumping out the contaminated mixture in condenser line (around
        \cmd{V4}) and still line (\cmd{V3}):} \cmd{\red{ensure that scroll is
        only pumping through V21 and that there is no mixture in the DR loop.
        The mixture exists between the collection tank and valves v10 and v5}
        \ira open v17, v3, V2 (to equalise pressure across the big valve) to
        pump the still side and V4 to pump the condenser line side}. \red{V18 is
        very small and hard to pump through};
  \item \textbf{Start pumping the trap} \cmd{\ira \red{close V14, V16} \ira open
        V17 and V7} (\cmd{V21} will still be open) \ira \cmd{wait 15-30
        minutes}.

        When we circulate the helium in the cycle, we pass it through the
        Nitrogen trap (the tank). Nitrogen, and oxygen will be condensed in this
        trap, so only volatile things like hydrogen and out helium will pass
        through. This means that at the capillaries we don't have
        oxygen/nitrogen plugs forming.

        At room temperature we must pump the trap to remove the gases that we
        adsorbed onto the carbon mesh inside the trap.

  \begin{framed}\noindent
    \red{Position the trap in the the can! DO NOT TAKE OUT EVEN WHEN TOPPING
      UP!}
  \end{framed}

  \item \cmd{\red{Close {V17} and {V7}. Pump the can again by opening V16 \ira
        V14. Wait until \quote{P6} = 1mbar}};
  \item \textbf{Activate the turbo pump:} \red{Close V14, V16, V21} \ira
        \cmd{Open {V23} \ira turn on Turbo2};
  \item \cmd{Go outside and press start/stop on the left-most bottom box \ira
        Open the dump valve by turning the black knob (which you cannot see)
        clockwise};
  \item \cmd{Open V22, {V16, {V14}}};
  \item \cmd{Turn on P1 on via the MaxiGauge board};
  \item \cmd{Dip the trap into the nitrogen tank};
  \item \cmd{After getting $ 3\times 10^{-3}\,$mBar \ira programming \ira load \ira
        installation package$\backslash$control scripts $\backslash$with extra turbo
        $\backslash$LD\_auto\_cooldown\_wlN2\_extra\_turbo\_V1\_21\_V23\_NOT\_open \ira
        run};
  \item \textbf{Good parameters are 17\ideg input water, 33\ideg output water,
        35\ideg oil colour.}\red{If required, go to pumps in back of room, and
        select constant pressure.}
  \item \red{In the morning the can should have been pumped already (V14-16-21
        closed). We need to close the turbo and scroll pump \ira \cmd{Go outside
        and switch turbo off \ira close turbo on computer panel \ira close
        backing V23 \ira close \quote{scroll pump}}}
  \item Sometimes on the morning after cooldown, you will see that the machine
        stops waiting 60seconds for \texttt{State 210} (normally this passes by
        midnight) then means that the large can is not at a low enough pressure.
        This can be sidestepped by removing the hard constraint on the low
        pressure (probably due to scroll pump vacuum seal not being that great)
        which is done in the program
        \verb|LD_auto_cooldown_wlN2_extra_turbo_V1_21_V23_NOT_open_210_4pfe-5|.
        You will need to check \verb|read_temperature.vi| to see how long until
        4K is reached and adjust the waiting time in the program.
  \item Sometimes, if you want to skip the 29 hour wait that occurs afterwards
        (pulse tube is expected to cool the system by itself to around 4K) you
        can launch the \verb|PPC_no_wait| to go straight to \verb|State 300|
        when mixture starts to get injected.
\end{enumerate}

\subsection{Mixing chamber circulation}
\label{sec:mixing-chamb-circ}

So, the first part of the cooling process is done with the pulse tube, cooling
to 5K, after which the He3 is pumped through He4 in the mixing chamber.
\red{This is driven on the right-hand-side of the panel, and it's the second
  turbo that causes this cirulation.}

In order for there to be enough He3 circulation, \red{\textbf{we actually need
    to heat the still stage so that the mixing chamber cools quicker.}}

\begin{enumerate}
  \item Thus, once still temperature (Ch5) reaches 600\,mK (and flow rate lowers
        to 30\,mmol/s) \ira \cmd{set ``Heat Analog2/Still'' to 10\,MW};
  \item \red{\textbf{Make sure flow rate is 60\,mmol/s}};
  \item \red{\textbf{Make sure still temperature is approximately 850\,mK}}.
\end{enumerate}

\noindent This will ensure that the mixing chamber gets enough He3 circulation
to cool to the base temperature of 13\,mK.

\subsection{Anomalous stopping}
\label{sec:anomalous-stopping}

Sometimes the system has to be stopped in an intermediate state - you can track
the cooldown progress in the \verb|read_temperature.vi| program and aligning the
current temperatures (red white) with those from the previous run (blue and
green).

There are two regions:
\begin{itemize}
  \item Pules tube cooldown - steady downwards line;
  \item Mixture being injected into the circulation loop. Happens 30 times, at
        which point temperature actually increases;
  \item The mixture being injected via the compressor, which lowers temperatures
        again;
  \item The evaporative cooling with full cycling of the mixture which reaches
        the base pressure.
\end{itemize}

If there is a deviation at some point (most commonly pulse tube cooldown stage)
and system needs to be shut down (commonly because there is a leak in the can
and pressure is $10^{-3}$ instead of $10^{-4}$) then the shutdown script below
will not work, as system is in an anomalous state.

\begin{framed}\noindent
  \red{The most important thing to do, is to collected the He3-He4 mixture into
    the mixture tank and the \texttt{v10-v5} region! The mixture is present if
    the mixture has been injected OR circulation has already begun.}
\end{framed}

\begin{enumerate}
  \item Turn on the scroll pump 1, to begin sucking the mixture out into the
        \texttt{v5-v10} region. Open up \texttt{v10} and \texttt{v13} to allow
        mixture to collect in the region, \texttt{V4} to suck the mixture from
        the input line, \texttt{V3} to pump the output line, \texttt{V2} to
        engage P2 to get pressure reading;
  \item When pressure in P2 stabilised close V3, V2, V10, scroll and V13.
  \item Finally can admit $5\,\text{mBar}$ of gas via vent into P1 to cool up
        the heating, or it can take a week
\end{enumerate}


\subsection{Shutting down}
\begin{enumerate}
  \item \red{Turn down current and shut down all amplifiers};
  \item \cmd{\quote{Maxigauge} \ira \quote{sensor P1} \ira \quote{off}} to shut
        down sensors during warmup;
  \item In the program load \verb|warmp_upV1_2| recipe \ira run;
  \item \cmd{\red{When \quote{MaxiGauge} \ira \quote{Channel 5} reads 800\,mBar
        get readt}};
  \item \cmd{Proceeding clockiwse, close all of the values in the cirulation
        cycle V7\ira V4\ira V1\ira V3\ira V10 \ira Scroll \ira V13};
  \item \cmd{Remove trap from the can. \red{Close the can with the lid}};
  \item \cmd{Turn off the BlueFors little box};
  \item \cmd{Go outside and close the dump valve by turning black handle (which
        you can't see) clockwise (from its perspective).} All of the helium will
        be trapped in the dump, so that it can be reused in the next cycle;
  \item After a few days, you can vent. \cmd{\quote{V19} \ira \quote{V16} \ira
        \quote{V14}.}
\end{enumerate}

 \subsection{Pumping the trap}
 The trap, which distills all kinds of gasses that leak into the Helium system,
 needs to be pumped before the next cooldown:
 \begin{enumerate}
   \item \cmd{Make sure the trap is out of the canister};
   \item \cmd{\quote{V2 Scroll} \ira V21 \ira V17 \ira V7}. \red{Wait for 1
         hour!}
   \item \cmd{V7 \ira V17 \ira V21 \ira \quote{V2 Scroll}}.
 \end{enumerate}

 \subsection{Heating up the cell}
 If we want to increase the temperature in the cell, we need to apply the heater
 in the blue Force program. Standard: Control channel = 6, heater = current,
 heater resistance = 120, puase time = 60, proportional = 10, integral = 2,
 derivative = 0.
 \begin{enumerate}
   \item \quote{Maxigauge} \ira \cmd{turn off 1, 2,5 } \ira the temperature
         readings on the box should read \quote{disable};
   \item \cmd{\quote{Heater setup} \ira \quote{control mode} \ira
         \quote{closed}};
   \item \cmd{Set the \quote{setpoint} temperature you want};
   \item \cmd{change the \quote{heater range} current \red{1-10mA} depending on
         how fast you are hating} \red{You may need to increase the
         \quote{Heater Limit}, as it acts as the safety stopper (to not
         overshoot the current).};
   \item \red{\quote{Write settings}};
   \item \cmd{Monitor temperature and make sure not to overshoot.}
   \item \cmd{\quote{Heater setup} \ira \quote{control mode} \ira \quote{off}}
         \ira \quote{Setup} \ira \cmd{turn on 1, 2,5 }
 \end{enumerate}

 \subsection{Computer monitoring BlueForce}
 \label{sec:comp-monit-bluef}

 \begin{enumerate}
   \item To connect to the BlueForce logs, \cmd{log 192.168.0.4} with password
         \cmd{resonator1}
   \item To access monitor connect \cmd{TightVNC viewer} with password
         \cmd{qubit2}
 \end{enumerate}
 \newpage
