\section{Chalmers Optical 213 Lamp}
  Follow the manual for startup.of lamp.
  \cmd{Power \mi{on} \ra when \mi{Ready} is shown press \mi{CP}\ra when \mi{start} is shown press \mi{start}}
 
  \subsection{Loading mask}
   \begin{enumerate}
   	\item \cmd{Get the correct chuck and attach it to the vacuum tube.} Pull on red screw to release the tube.
   	\item \cmd{Click \mi{change mask} \ra \mi{enter}} to turn off the vacuum;
    \item \cmd{Position mask in the check \ra \mi{enter}} to turn vacuum on \ra \cmd{slide the chuck into machine};
   \end{enumerate}

  \subsection{Loading program}
   \begin{itemize}
   	\item \cmd{\mi{Select program}\ra up and down arrows to select \mi{soft},\mi{loVac} etc\ra \mi{select program}} to stop selection. Soft, Hard, LoVac, Vac are in order of increasing lithography accuracy (from 3$ \mu m $ to 500nm);
   	\item \cmd{\mi{Edit program} \ra change \textbf{exposure time} and \textbf{working distance} (typically 20$ \mu m $), 10 sec pre vacuum\ra\mi{edit program}} to set.
   	\item \red{MAKE SURE THAT FLOOD IS OFF!! Or exposure will begin straight after loading};
   \end{itemize}

  \subsection{Loading samples}
   \begin{enumerate}
   	\item \cmd{Press \mi{load} \ra put sample on plate \ra \mi{Enter} to turn on vacuum \ra slide in \ra \mi{Enter} to raise the bar};
   	\item WEC performed (bringing plate to the mask);
   \end{enumerate}

  \subsection{Aligning}
   By this stage we should be in alignment mode. Choose \mi{split field option}, separate the objectives by turning handles on side of microscope, fine focus just above the lenses. Intensity also above lenses. Rotate microscope with knob on the top.
   \begin{enumerate}
   	\item \cmd{Turn dial \mi{TSA}};
   	\item \cmd{Use arrows to move to first marker \ra \mi{Set prefference} to remember position};
   	\item \cmd{Move to second marker \ra \mi{Scan}} to move back to first position;
   	\item \cmd{Turn X-Y dials to center the marker};
   	\item \cmd{Press \mi{scan} \ra move to second marker \ra turn Theta dial} so that pattern shift halfway to correct position \cmd{\ra \mi{scan} to move back to first marker;}
   	\item \cmd{Repeat above steps};
   	\item \cmd{Once alignment looks good enough press \mi{Alignment check} to bring sample close to mask \ra change magnification \ra\red{perform check!! BUT NO MOVEMENT} \ra press \mi{Alignment check} to move again.}
   	\item \red{PRESS EXPOSURE TO EXPOSE};
   \end{enumerate}
  
  Automatic unloading. \cmd{\mi{Change mask} \ra \mi{enter} \ra unload \ra \mi{TSA} off}.
 \newpage
 