\section{Chalmers Logitech polisher}
  Station is used for thinning and polishing wafers. It is located in the room leading out the the corridor that goes along the clean room. \red{Put on overshoes and gloves}.
  
  \subsection{Sticking wafer to glass plates}
  \begin{enumerate}
  	\item \cmd{Clean small circular disk with \mi{EcoClean}};
  	\item \cmd{Put samples on glass and place on heater at 50\ideg \ra swear wax on sides of samples to stick it on.}
  \end{enumerate}
 
  \subsection{Prepare machine}
  \begin{enumerate}
  	\item \cmd{Turn on blue vent above machine};
  	\item \cmd{Place large glass disk on machine};
  	\item \cmd{Prepare \mi{$ Al_{2}O_{3}, 9\mu m$ 100ml of powder for 750 ml of water} in barrel. \red{Mix together and scrape bottom with screwdriver}};
  	\item \cmd{Put barrel with liquid in holder \ra open the lid slightly \ra attach the dropper} (looks like a half pipe with a wire sticking out) \cmd{and screw it in.};
  	\item \cmd{Attach plate wiper on the side};
  	\item \cmd{Cover disk with \red{distilled water} \ra then start dropping the grinding liquid} \red{DISK MUST ALWAYS BE WET TO AVOID DAMAGE};
  	\item \cmd{Turn on \mi{Green Switch} button to activate the machine \ra \mi{options} \ra \mi{lap}.};
  	\item To begin calibrating \cmd{get the small thickness sensor and place it on the flat graphite tablet \ra attach cable to machine from sensor \ra Click \mi{setup} and you will see a scale from -10 to 10 that measures the concave (edge of mirror is higher) or convex (edge of mirror is lower) of the mirror. \red{SET TO ZERO} since the graphite plate is absolutely flat}. If the reading is close to $ \pm10 $ then read manual oh how to calibrate;
  	\item \cmd{Switch on \mi{abrasive autofeed}} so the barrel begins rotating;
  	\item \cmd{Grab Fork holder and place it on one of the rods. Put the calibrated sensor into it \ra put weight ring on top}, so that the rollers are free to move. May want to change to shorter cable. 
  	\item \cmd{Then place glass grinder with its holder onto other rod and add a weight on top \ra start up the machine and monitor the concave/convex monitor \ra move the grinder to the middle if the mirror is too concave, or to the edge if it is too convex \ra spin at 20rpm until the monitor is near zero};
	\item \cmd{Wait 5 minutes}
  \end{enumerate}

  Remove grinder and wash in ultrasound. The glass mirror is now ready to grind.
  
  \subsection{Thinning wafer}
   \begin{enumerate}
   	\item \cmd{Run \mi{system check}} which will move the rods;
   	\item Measure wafer thickness by using pump device. Measure on glass \ra set to zero \ra measure on plate. \red{Drop the pin very carefully!};
   	\item \cmd{Place the wafer on the big holder \ra attach vacuum pipe \ra squeeze the big holder spring, so that the sample is lower than the outer edges of the device \ra transfer onto disk and position};
   	\item \cmd{Reset the thickness and start up the machine.} Thickness is evaluated by calculating the spring extension inside the device as the wafer is thinned;
   	\item \cmd{Stop machine \ra rinse wafer in water \ra clean the grinder and thickness monitor with ultrasound, rest with water \ra \red{ remove solution bottle from top!}};
   \end{enumerate}

  \subsection{Polishing}
   \begin{enumerate}
   	\item \cmd{Make sure all components are cleaned from the 9$ \mu m $ solution that would destroy the polish \ra take the \mi{polish disk} and drain it with water};
   	\item \cmd{Attach the small thickness sensor \ra attach the doughnut shape metal to the other side \ra spin and spray on the polish solution until disk is evenly coated};
   	\item \cmd{Load the sample onto the big holder \ra turn on vacuum \ra squeeze it and transfer to plate};
   	\item \cmd{Start rotating \ra every 40 seconds squeeze more liquid};
   	\item \red{Once done, immediately remove holder \ra turn off vacuum and wash to remove the chemical creating the polish};
   \end{enumerate}

   \cmd{\red{Wash everything in water \ra turn off vent}}.
   
   To remove from glass \cmd{Place in 150\ideg EcoClean \ra EcoClean \ra Acetone \ra IPA.}

 
 
 
 \newpage
 