% -*- TeX-master: "../fat_manual.tex" -*-
\section{RHUL The chook-chook}
\iframe{Valve 2 -  its the equlibrator for V1 -  you need the same pressure on  either side of
  V1, and  you use  V2 to do  this.  Then, the  can open  V1.}  \iframe{The cooling  system is
  composed of two parts
  \begin{itemize}
  \item The pulse tube that fires in helium and expands it - it uses the big compressor in the
    shed
  \item The circulating cycle of He3 that is pumped out of He4. This is the big contour on the
    right of the big  screen. P3 monitors the pressure before  the capillary constriction that
    this mixture is funneled through.
  \end{itemize}
}

\subsection{Pumping}
System needs to be pumped to avoid formation of ice when it is cooled.
\begin{enumerate}
\item Can load the two blueforce programs on the desktop;
\item \cmd{First stop venting by closing valves 14, 16, 19};
\item \cmd{Close the cases, with the stitch facing the far wall of the lab};
\item \cmd{Check the pressure is > 40mBar on the cylinder in the corner.}
\item \cmd{Refill the trap with nitrogen so its full}. The trap will absorb gases that are not
  Helium - they liquify? Eventually we need to replenish it;
\item \cmd{Turn on the \mi{Scroll Pump 2} \ra V21, V16, V14} for rough pumping. \red{\cmd{Wait
      until \mi{P6} reads 1mbar}}.
\item \textbf{Start pumping the  trap} \cmd{\ra \red{close V14, V16} \ra  open {V17} and {V7}}
  (\mi{V21} will still be open) and wait 15-30 minutes.
  	
  When we circulate the helium in the cycle,  we pass it through the Nitrogen trap (the tank).
  Nitrogen, and oxygen will  be condensed in this trap, so only  volatile things like hygdroen
  and  out helium  will  pass  through. This  means  that at  the  capillaries  we don't  have
  oxygen/nitrogen plugs forming.
  	
  At room  temperature we must  pump the trap  to remove the gases  that we adsorbed  onto the
  carbon mesh inside the trap.
  	
  \red{Position the trap in the the can! DO NOT TAKE OUT EVEN WHEN TOPPING UP!}
  	
\item \cmd{\red{Close {V17}  and {V7}. Pump the can  again by opening V16 \ra  V14. Wait until
      \mi{P6} = 1mbar}};
\item \textbf{Activate the turbo pump} \red{Close V14,  V16, V21} \ra \cmd{Open {V23} \ra turn
    on \mi{Turbo2} \ra open {V22}, {V16, {V14}}}
\item \cmd{Go outside and press start/stop on the left-most bottom box \ra Open the dump valve
    by turning the black knob (which you cannot see) clockwise};
\item \cmd{in the lab turn \mi{P1} on via the \mi{MaxiGauge} board}.
\item \cmd{dip the trap into the nitrogen tank}.
\item  \cmd{After  getting  $  3\times   10^{-3}\,$mBar  \ra  \mi{programming}  \ra  \mi{load}  \ra
    \mi{installation   package$   \backslash   $   control   scripts   $   \backslash   $   with   extra   turbo
      $ \backslash $ \newline LD\_auto\_cooldown\_wlN2\_extra\_turbo\_V1\_21\_V23\_open} \ra run}
\item  \textbf{Good parameters  are 17\ideg  input water,  33\ideg output  water, 35\ideg  oil
    colour.}\red{If required, go to pumps in back of room, and select constant pressure.}
\item \red{In the morning the can should  have been pumped already (V14-16-21 closed). We need
    to close  the turbo and  scroll pump \ra  \cmd{Go outside and  switch turbo off  \ra close
      turbo on computer panel \ra close backing V23 \ra close \mi{scroll pump}}}
\end{enumerate}

\subsection{Mixing chamber circulation}
\label{sec:mixing-chamb-circ}

So, the first  part of the cooling process is  done with the pulse tube, cooling  to 5K, after
which  the He3  is pumped  through He4  in the  mixing chamber.   \red{This is  driven on  the
  right-hand-side of the panel, and it's the second turbo that causes this cirulation.}

In order  for there to be  enough He3 circulation,  \red{\textbf{we actually need to  heat the
    still stage so that the mixing chamber cools quicker.}}

\begin{enumerate}
\item Thus, once still temperature (Ch5) reaches  600\,mK (and flow rate lowers to 30\,mmol/s)
  \ira \cmd{set ``Heat Analog2/Still'' to 10\,mW};
\item \red{\textbf{Make sure flow rate is 60\,mmol/s}};
\item \red{\textbf{Make sure still temperature is approximately 850\,mK}}.
\end{enumerate}

\noindent This will ensure that the mixing chamber  gets enough He3 circulation to cool to the
base temperature of 13\,mK.

\subsection{Shutting down}
\begin{enumerate}
\item \cmd{\mi{Maxigauge} \ra \mi{sensor P1} \ra \mi{off}} to shut down sensors during warmup;
\item \cmd{In the program load \mi{warmup} recipe \ra run};
\item \cmd{\red{When \mi{MaxiGauge} \ra \mi{Channel 5} reads 800\,mBar get readt}};
\item \cmd{Proceeding clockiwse, close  all of the values in the  cirulation cycle V7\ra V4\ra
    V1\ra V3\ra V10 \ra Scroll \ra V13};
\item \cmd{Remove trap from the can. \red{Close the can with the lid}};
\item \cmd{Turn off the BlueFors little box};
\item \cmd{Go outside and  close the dump valve by turning black handle  (which you can't see)
    clockwise (from its perspective).}  All of the helium will be trapped in the dump, so that
  it can be reused in the next cycle;
\item After a few days, you can vent.  \cmd{\mi{V19} \ra \mi{V16} \ra \mi{V14}.}
\end{enumerate}

 \subsection{Pumping the trap}
 The trap, which  distills all kinds of gasses  that leak into the Helium system,  needs to be
 pumped before the next cooldown:
 \begin{enumerate}
 \item \cmd{Make sure the trap is out of the canister};
 \item \cmd{\mi{V2 Scroll} \ra V21 \ra V17 \ra V7}. \red{Wait for 1 hour!}
 \item \cmd{V7 \ra V17 \ra V21 \ra \mi{V2 Scroll}}.
 \end{enumerate}
 
 \subsection{Heating up the cell}
 If we want to increase  the temperature in the cell, we need to apply  the heater in the blue
 Force program.   Standard: Control channel  = 6, heater =  current, heater resistance  = 120,
 puase time = 60, proportional = 10, integral = 2, derivative = 0.
 \begin{enumerate}
 \item \mi{Maxigauge}  \ra \cmd{turn  off 1,  2,5 } \ra  the temperature  readings on  the box
   should read \mi{disable};
 \item \cmd{\mi{Heater setup} \ra \mi{control mode} \ra \mi{closed}};
 \item \cmd{Set the \mi{setpoint} temperature you want};
 \item \cmd{change  the \mi{heater range} current  \red{1-10mA} depending on how  fast you are
     hating} \red{You  may need to increase  the \mi{Heater Limit},  as it acts as  the safety
     stopper (to not overshoot the current).};
 \item \red{\mi{Write settings}};
 \item \cmd{Monitor temperature and make sure not to overshoot.}
 \item \cmd{\mi{Heater setup} \ra \mi{control mode} \ra \mi{off}} \ra \mi{Setup} \ra \cmd{turn
     on 1, 2,5 }
 \end{enumerate}

 \subsection{Computer monitoring BlueForce}
 \label{sec:comp-monit-bluef}

 \begin{enumerate}
 \item To connect to the BlueForce logs, \cmd{log 192.168.0.4} with password \cmd{resonator1}
 \item To access monitor connect \cmd{TightVNC viewer} with password \cmd{qubit2}
 \end{enumerate}
 \newpage
